DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-08-30 ase2017/paper.tex
added text about experiments to be evaluated
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Our evaluation consists of $18$ SISO control system benchmarks extracted
from the literature~\cite{abate2017, abatecav2017, bouabdallah, acrobot,
cstr, KOKOTOVIC198023, gajic2008optimal, Franklin15, maglev, converters,
CTMS, DBLP:journals/tc/BessaIPCF17, DBLP:journals/dafes/BessaICF16}, which
include physical plants for an unmanned aerial vehicle (UAV), a cruise
control system, a spring-mass damper, a satellite, a direct current (DC)
servo motor, a helicopter, the inverted pendulum, a pendulum, magnetic
suspension, a magnitezed pointer, 1/4 car suspension, a computer tape
driver, a flexible beam, a guidance system, a US Coast Guard cutter, a
continuous stirred tank reactor, a voltage regulator, and an acrobot control
system.

>>>>

Our evaluation consists of $18$ SISO control system benchmarks extracted
from the literature~\cite{abate2017, abatecav2017, bouabdallah, acrobot,
cstr, KOKOTOVIC198023, gajic2008optimal, Franklin15, maglev, converters,
CTMS, DBLP:journals/tc/BessaIPCF17, DBLP:journals/dafes/BessaICF16}, which
include physical plants for an unmanned aerial vehicle (UAV), a cruise
control system, a spring-mass damper, a satellite, a direct current (DC)
servo motor, a helicopter, the inverted pendulum, a pendulum, magnetic
suspension, a magnetized pointer, 1/4 car suspension, a computer tape
driver, a flexible beam, a guidance system, a US Coast Guard cutter, a
continuous stirred tank reactor, a voltage regulator, and an acrobot control
system.
